### 2022-03-08 paper/output/document/thesis_5_discussion.tex
my back hurts

%
\begin{isabellebody}%
\setisabellecontext{thesis{\isacharunderscore}{\isadigit{5}}{\isacharunderscore}discussion}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Discussion\label{discussion}%
}
\isamarkuptrue%
%
\isamarkupsubsection{Automated Moral Agents in Practice \label{AIethics}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In Chapter \ref{applications}, I demonstrated that my system is capable of performing sophisticated,
nuanced ethical reasoning. In this section, I outline the additional components necessary for my system
to guide AI agents. My work on automating the categorical imperative 
could serve as one component of a partially or fully artificial ethical reasoner, or an ``ethical AI.''
Specifically, my system is a categorical imperative library that takes as input the logical representation 
of a maxim and returns its moral status (if it is obligatory, prohibited, or permissible).
As it stands, my project can evaluate the moral status of maxims represented in my logic and potentially 
serves as one component of an ``ethics engine'' that an AI agent could use to make ethical decisions.
For example, my system could be combined with an input parser to translate moral dilemmas as represented 
to the AI agent into maxims in my logic. An output parser could translate my system's output
into a prescription for action that the AI agent could act on. Figure \ref{fig:AIengine} depicts the 
workflow of this example ethics engine.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{figure}
\centering
\includegraphics[scale=0.5]{AI_engine.png}
\caption{An example of an ethics engine for an artificial agent, which begins with a moral dilemma, 
passes it through an input parser, applies the automated categorical imperative test, and then processes the 
output using an output parser. I contribute the automated categorical imperative component.} \label{fig:AIengine}
\end{figure}
%
\begin{isamarkuptext}%
In this workflow, an AI agent is faced with a moral dilemma in some internal representation. The input
parser translates this internal representation into an appropriate logical representation, i.e. 
a circumstance, act, goal tuple. The output parser translates the output of the categorical imperative
library (the moral status of the maxim as obligatory, prohibited, or permissible) to a prescription for
action. In order for my system to be used in an AI agent using the workflow
above, future work would need to develop such input and output parsers.

The input parser must translate a complex real-world situation into a flat, logical representation.
This requires that the input parser determine which circumstances are ``morally relevant''
for a maxim, a controversial judgement.
There is robust debate in the literature on the circumstances that should be considered when formulating a maxim, 
inspired by a common objection to Kantian ethics. The``tailoring objection'' is the worry that arbitrarily specific 
circumstances render any maxim universalizable. For example, the maxim ``When my name is Lavanya Singh 
and I am wearing a purple shirt and it is November 26th, I will lie in order to get some easy cash'' 
passes the universalizability test. Even if this maxim is willed universally, the circumstances are so 
specific that lying will not become the general mechanism for getting easy cash, so the lender will 
believe my lie and the maxim will remain effective. By tailoring the circumstances, any maxim can 
evade universalization.

@@

While this view has intuitive appeal, it raises the question of how we can determine
which circumstances are morally relevant. O'Niell answers this question by noting that the Formula of Universal Law is 
a ``test of moral worth rather than of outward rightness'' \citep[98]{constofreason}. The FUL is a way 
for an agent to decide how they should behave, not for a third-party to judge their behavior. Ethics is 
a personal proces and the FUL is designed to help agents internally make decisions. Because agents use 
the FUL to evaluate their own behavior, the test is at its 
best when they make a good faith effort to isolate the \emph{principle} of their action, rather than some
``surface intent'' \citep[87]{constofreason}. The FUL is supposed to determine if an agent's principle of action
is universally consistent, so it is most effective when an agent accurately formulates the principle
they act on. Circumstances are morally relevant if they reflect the way that the agent is 
thinking about their own action. In the example above, the circumstance of wearing a purple shirt doesn't reflect
the principle of the liar's action. Its inclusion is a disingenous attempt to evade the universalizability
test, but because the FUL is a test of personal integrity, it cannot withstand this kind of mental
gymnastics.

@@

This representational question is one of the biggest challenges to using my categorical imperative library
in an AI ethics engine. One solution is for a human being to perform the role of the input
parser. Once an AI agent stumbles onto an ethical dilemma, a human being could take over, formulate 
the right question, and feed it into the categorical imperative library to see what action the categorical 
imperative would prescribe. For proponents of the ``human-in-the-loop'' model of AI ethics, in which 
ethical AI requires that humans guide machines \citep{loop}, this kind of human involvement may be a feature.
The outcome of the universalizability test will depend on how the human formulates the maxim; if the 
human puts garbage into the test, the test will return garbage out.

@@

My system's output could be converted into some actionable, useful response with another output parser, 
and then passed back to the AI agent. For example, if the AI agent is equipped to evaluate natural 
language prescriptions, the status of the maxim could be parsed into a natural language sentence. The 
input parser, categorical imperative library, and output parser together constitute an ``ethics engine'' 
that AI developers could use as a black box implementation of an ethical theory.

@@

Consider the example badly-formed maxim, ``When eating breakfast, I will eat breakfast in order to 
eat breakfast.'' There is something empty about this maxim because acting on it could never result in 
any action. If an agent adopts this maxim, 
they decide that, in the circumstances ``eating breakfast'' they will perform the act ``eating breakfast''
for the purpose ``eating breakfast.'' In these circumstances, the act has 
already been performed! Adopting this maxim as a law to live by does not change how you live. If you adopt 
this maxim, then when you are eating breakfast, you eat breakfast, but this statement is already tautologically true.

@@

Another related worry has to with maxims that we think are prohibited. Consider the maxim modified to 
read ``When dancing and seeing a child drowning, I should dance for the sake of dancing.'' Clearly this 
maxim is fit for moral evaluation, and we expect a moral theory to prohibit this maxim. The circumstances 
``When dancing and seeing a child drowning'' appear to entail the act of dancing, and the maxim thus 
appears badly-formed. Once again, this maxim is formulated incorrectly. In this case, the question 
that the agent is actually asking themselves is ``should I continue dancing?'' That is the 
maxim that they will adopt or reject. They want to know if they should stop dancing and go help the child. 
Dancing at the current moment and dancing at the next moment are different acts, and the circumstances 
imply the former but not the latter. A badly-formed maxim would have circumstances and act both 
``dancing at moment t,'' but this maxim has circumstances ``dancing at moment t'' and act ``dancing 
at moment t+1.''

@@

In the previous section, I defined badly formed maxims, a philosophical concept that I discovered
using computational ethics. In this section, I demonstrate the implications of this concept for a 
philosophical debate to demonstrate that computational ethics can result in insights with real 
philosophical weight. I use badly formed maxims to resolve the tension between self-doubt and self-respect. 
This debate originated in epistemology, which values doubting your beliefs but also rationally requires
that you believe that you are not mistaken (else you should update your beliefs). 
Self-doubt and self-respect also compete in ethics, where questioning your judgements is valuable but 
questioning a commitment as you make it is impossible. Self-doubt and self-respect appear 
irresolvably opposed until they are understood through the lens of badly formed maxims. I argue that naive
conceptions of self-doubt are badly formed maxims in disguise. If we reformulate these maxims to be well-formed,
the tension between self-doubt and self-respect dissolves, and it becomes clear that both concepts can
co-exist, as we intuitively desire. I sketch the details of this argument in the rest of this section.

@@

While most philosophers accept some version of SR\footnote{Christensen cites \citet{vanfraasen}, 
\citet{vickers}, and \citet{koons}.}, 
Roush argues that the principle must be modified in order to account for healthy epistemic 
self-doubt. She argues that, while pathological second-guessing is correctly criticized, we are generally 
imperfect beings, and some sensitivity to our own limitations is a virtue \cite[2]{roushselfhelp}. Even Christensen 
acknowledges that total self-confidence is an epistemic flaw \cite[1]{christensen}. Thus, there is tension between the rational
requirement to respect our authority as believers and the practical reality that we are often wrong.

@@

To resolve this tension, I return to my earlier example of a dancer. Imagine Sara is dancing at a 
weddding, when, in a moment of angst, she asks herself, ``Should I really be dancing right now?'' 
It seems that she asking if the maxim, ``When dancing at your friend's wedding, dance for the sake 
of dancing'' is a permissible maxim to act on. Notice that the maxim in question is badly-formed: the 
circumstance ``when dancing at a friend's wedding'' implies the act ``dance.'' Because this is a 
badly-formed maxim, it cannot be the maxim that she is questioning, for adopting
this maxim could not have changed her behavior at all. Sara is wondering if her behavior is permissible, but
any conclusions about the permissibility of a badly-formed maxim would not help her. This is because 
the maxim has no effect on her action and because any such permissibility would be a foregone conclusion,
since she has already adopted the maxim. Thus, under the interpretation of self-doubt as a badly-formed 
maxim, the tension between ESR and ethical self-doubt seems irresolvable. Those committed to this 
interpretation must abandon one principle or the other, since committing and questioning are incompatible.

To resolve this issue, I turn to another interpretation of ethical self-doubt. Under this interpretation, 
when Sara asks, ``Should I really be dancing right now?'' she wants to know if the maxim that 
resulted in the current moment when she is on the dance floor was the right thing to will. She is 
asking if she made the right decision in the past, when she decided to dance. The maxim that initiated 
the dancing may be something like ``When at a wedding, dance for the sake of dancing.'' This is the maxim 
that she is currently acting on, not the badly-formed maxim  from above. Under this interpretation, 
there is no tension at all between self-doubt and self-respect. It is perfectly valid for a reasoner 
to doubt their prior moral judgements, just as it is perfectly rational for a believer to doubt their 
past beliefs \cite[3-4]{christensen}. Such doubt does not undermine the reasoner's decision-making 
capacity and is thus perfectly consistent with ethical self-respect.

The tension between ESR and ESD arises from a misreading of questions of self-doubt as questions about 
the evaluation of badly-formed maxims. A question of self-doubt cannot refer to a badly-formed maxim and must 
instead refer to a well-formed maxim about the agent's past decision-making. As seen before, cases where 
agents appear to ask themselves about badly-formed maxims are mistaken about the maxim in question, because 
such a question could never yield a useful answer for a practical reasoner.

By recognizing that the naive version of ethical self-doubt is a badly formed maxim, I realized 
that there is something wrong with its formulation and modified it to resolve the above debate. 
This demonstrates a larger meta-pattern in Kantian reasoning: many debates in Kantian philosophical
literature revolve around incorrectly formulated maxims, so the insight about badly
formed maxims is significant. Much of the work of a Kantian ethicist is formulating an
appropriate maxim, and badly-formed maxims define one boundary condition for this task.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{An Argument For Computational Ethics%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
The insight above is an example of the kind of philosophical progress that can be 
made using computational tools and serves as evidence for the power of computational ethics. The 
idea that the FUL can only hold for well-formed maxims would have been
incredibly difficult to discover without a computer. I discovered it while formulating the FUL because 
Isabelle's proof-finding tools look for edge cases like badly-formed maxims. Badly-formed maxims are 
interesting because they are the kind of thing that is usually ignored in ordinary philosophical inquiry. 
Philosophers usually assume that we are not discussing badly-formed maxims because, as argued above, 
they are not the kind of thing that is immediately relevant to ethics. Computational tools like Isabelle
require that assumptions like the exclusion of well-formed maxims are made precise, and thus force 
philosophers to understand their arguments in a new way. This example demonstrates the contributions
that computational ethics makes: it can quickly check edge cases and it requires that all assumptions be
made explicit and precise.

I do not argue that computational ethics uncovers philosophical insights that humans are incapable 
of reaching. Instead, I claim that insights like the one about the well-formed maxim are much easier
to reach with computational tools. Badly-formed maxims are usually ignored in philosophical discussion 
and would have been much more difficult to understand without the help of a computer. Computational 
tools prompt philosophers to ask new questions that 
lead to insights, and can thus serve as another tool in a philosopher's arsenal, like a 
thought experiment or counterexample.\footnote{Even if computational ethics is possible, some may 
worry that it sacrifices something important about philosophical inquiry. I discuss this concern in Appendix 
\ref{academicphilosophy}.}

@@

Computational ethics is at its infancy. The use of theorem provers in mathematics is just now beginning 
to make headway \citep{buzzardvideo}, even though theorem provers were first invented in the 1960's \citep{historyofITP}. 
In contrast, the first attempts to use theorem provers for ethics occurred in the last decade. The 
fact that this nascent technology is already helping humans reach non-trivial philosophical conclusions 
is reason to, at the very least, entertain the possibility of a future where computational ethics 
becomes as normal for philosophers as using a thought experiment.

@@

The above model of human-computer symbiosis demonstrates how computational ethics can augment human
ethical reasoning without replacing it. When deliberating over moral dilemmas, ordinary people can 
turn to computational tools for advice, like an ``Ask an Ethicist'' column. If we appeal to philosophically
faithful computational ethics like that implemented in this thesis, then this advice will synthesize 
decades of philosophical progress and is thus a way to apply philosophers' insights to ordinary life. 
Moreover, just as they do for philosophers, computers can help ordinary people approach ethical questions from a 
different perspective. Even interacting with my system requires the user to consider the action's maxim, 
which includes the circumstances, act, and goal. Making these components of action precise already changes
the user's perspective. Just as computational ethics can serve as a tool for academic philosophers to 
automate away tedium and achieve greater precision, it can do the same for ordinary human beings navigating
the world. Moreover, it also offers another way for the general public to access professional philosophy's
insights, and thus carries potential to improve our everyday reasoning.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Theoretical Objections to Automating Kantian Ethics \label{amapossible}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Many philosophers cringe at the idea that a computer could perform ethical reasoning or that the 
categorical imperative could provide an algorithm for moral judgement. For example, Rawls asserts, 
``it is a serious misconception to think of the CI-procedure as an algorithm intended to yield, 
more or less mechanically, a correct judgment. There is no such algorithm, and Kant knows this'' \citep[166]{rawlslectures}. 
Ebels-Duggan also claims, ``no one supposes that the Categorical Imperative provides a mechanical 
algorithm that delivers all by itself a complete account of what we ought to do in any given 
situation'' \citep[174]{ebelsduggan}. However unmechanical ethical reasoning
may seem, these claims are not obvious and require further justification. Philosophers who believe 
that mental activity completely determines moral reasoning must explain why computers can, in theory, 
simulate certain mental processes like arithmetic and language, but cannot perform ethical reasoning. 
Without a soul or God-based account of ethical reasoning, it is not obvious that it is theoretically 
impossible to automate ethical reasoning. After all, computers may eventually learn to simulate human 
mental activity entirely, as shown by progress in brain simulation \citep{brainsimulation}.

@@

In \emph{Universal Laws and Ends In Themselves}, O'Neill argues against the existence of an algorithm for
moral behavior. She points out that Kant draws an important distinction between a morally worthy maxim
and a morally worthy action: the latter requires a good will, or a will motivated by duty. She argues that, 
``Kant defines duty not (as would be common today) as outward performance of a certain sort, but as action
that embodies a good will'' \citep[345]{oneilluniversallaws}. Moral behavior doesn't just require performing
a ``good'' action, but it requires acting on a morally worthy maxim from the motivation of duty, or 
doing the right thing because it is the right thing to do. Moral behavior requires both a certain action 
(acting on a morally worthy maxim) and a certain motivation (the motivation of duty). It is this capacity 
for self-motivation that makes morality binding for rational beings; we must behave morally precisely 
because we have wills, or the ability to be motivated by ends
that we choose. Only rational beings have wills, so only rational beings can have good wills, or wills
motivated by duty, and thus only rational beings can behave morally. Under this understanding
of moral behavior, it seems unlikely that a computer could behave morally
since a computer does not have motivation in the same way as a human being. If a computer is not a fully rational
being, then it is not the kind of thing that can behave morally.\footnote{A parallel argument can also be made for virtue ethics. Virtuous
behavior requires not only a certain action, but also a certain disposition towards the action, so it seems
difficult for an AI agent to truly behave virtuously.}

@@

The challenge of mapping actions to maxims is a limitation of my system, but it is not insurmountable. In Section \ref{aiethics},
I argued that, before my system can be used in practice, it must be paired with an input parser that can
translate choices that an automated agent faces into maxims in a logic that my system can
evaluate. This need follows from the difficulty in mapping a potential action
to the maxim of action, whether concerning human action or machine action. As argued in Section \ref{AIethics},  
this is not an insurmountable obstacle for automated ethics and heuristic-based approaches could resolve
this issue. Determining the maxim of action is a challenge for Kantian human beings \citep{oneilluniversallaws}, 
so it is unsurprising that it is a major hurdle for automated Kantian agents.

@@

%:%63=33%:%

@@

%:%182=145%:%
%:%194=147%:%

@@

%:%207=153%:%
%:%219=155%:%

@@

%:%410=341%:%
%:%422=343%:%
%:%423=344%:%
%:%424=345%:%
%:%425=346%:%
%:%426=347%:%

@@

%:%496=410%:%
%:%508=412%:%
%:%509=413%:%
%:%510=414%:%
%:%511=415%:%

@@

%:%595=493%:%
%:%607=496%:%
%:%608=497%:%
%:%609=498%:%
%:%610=499%:%

@@

%:%717=605%:%
%:%718=606%:%
%:%719=607%:%

@@

%:%725=611%:%

>>>>

%
\begin{isabellebody}%
\setisabellecontext{thesis{\isacharunderscore}{\isadigit{5}}{\isacharunderscore}discussion}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Discussion\label{discussion}%
}
\isamarkuptrue%
%
\isamarkupsubsection{Automated Moral Agents in Practice \label{AIethics}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In Chapter \ref{applications}, I demonstrated that my system is capable of performing sophisticated,
nuanced ethical reasoning. In this section, I outline the additional components necessary for my system
to guide AI agents in practice. My work on automating the categorical imperative 
could serve as one component of a partially or fully artificial ethical reasoner, or an ``ethical AI.''
Specifically, my system is a categorical imperative library that takes as input the logical representation 
of a maxim and returns its moral status (if it is obligatory, prohibited, or permissible).
As it stands, my project can evaluate the moral status of maxims represented in my logic and potentially 
serves as one component of an ``ethics engine'' that an AI agent could use to make ethical decisions.
For example, my system could be combined with an input parser to translate moral dilemmas as represented 
to the AI agent into maxims in my logic. An output parser could translate my system's output
into a prescription for action that the AI agent could act on. Figure \ref{fig:AIengine} depicts the 
workflow of this example ethics engine.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{center}
\begin{figure}
\includegraphics[scale=0.43]{AI_engine.png}
\caption{An example of an ethics engine for an artificial agent, which begins with a moral dilemma, 
passes it through an input parser, applies the automated categorical imperative test, and then processes the 
output using an output parser. I contribute the automated categorical imperative component.} \label{fig:AIengine}
\end{figure}
\end{center}
%
\begin{isamarkuptext}%
In this workflow, an AI agent is faced with a moral dilemma in some internal representation. The input
parser translates this internal representation into an appropriate logical representation, i.e. 
a circumstance, act, goal tuple. The output parser translates the output of the categorical imperative
library (the moral status of the maxim as obligatory, prohibited, or permissible) to a prescription for
action. In order for my system to be used in an AI agent using the workflow
above, future work would need to develop such input and output parsers.

The input parser must translate a complex real-world situation into a flat, logical representation.
This requires that the input parser determine which circumstances are morally relevant
to a maxim, a controversial judgement. As mentioned in Section \ref{whatisamaxim},
there is robust debate in the literature on the circumstances that should be considered when formulating a maxim, 
inspired by the tailoring objection, a common criticism of Kantian ethics. Recall that the tailoring objection is the worry that arbitrarily specific 
circumstances render any maxim universalizable. For example, consider the maxim ``When my name is Lavanya Singh 
and I am wearing a purple shirt and it is November 26th, I will lie in order to get some easy cash.'' 
Even if this maxim is willed universally, the circumstances are so 
specific that lying will not become the general mechanism for getting easy cash, so the lender will 
believe my lie and the maxim will remain effective. By tailoring the circumstances, any maxim can 
evade universalization.

@@

While this view has intuitive appeal, it raises the question of how we can determine
which circumstances are morally relevant. O'Neill answers this question by noting that the Formula of Universal Law is 
a ``test of moral worth rather than of outward rightness'' \citep[98]{constofreason}. The FUL is a way 
for an agent to decide how they should behave, not for a third-party to judge their behavior. Ethics is 
a personal process and the FUL is designed to help agents make decisions. Because agents use 
the FUL to evaluate their own behavior, the test is at its 
best when they make a good faith effort to isolate the \emph{principle} of their action, rather than some
``surface intent'' \citep[87]{constofreason}. The FUL is supposed to determine if an agent's principle of action
is universally consistent, so it is most effective when an agent accurately formulates the principle
they act on. Circumstances are morally relevant if they reflect the way that the agent is 
thinking about their own action. In the example above, the circumstance of wearing a purple shirt doesn't reflect
the principle of the liar's action. Its inclusion is a disingenous attempt to evade the universalizability
test, but because the FUL is a test of personal integrity, it cannot withstand this kind of mental
gymnastics.

@@

This representational question is one of the biggest challenges to using my categorical imperative library
in an AI ethics engine. One solution is for a human being to perform the role of the input
parser. Once an AI agent stumbles onto an ethical dilemma, a human being could take over, formulate 
the right question, and feed it into the categorical imperative library to see what action the categorical 
imperative would prescribe. For proponents of the ``human-in-the-loop'' model of AI ethics, in which 
ethical AI requires that humans guide machines, this kind of human involvement may be a feature \citep{loop}.
The outcome of the universalizability test will depend on how the human formulates the maxim; if the 
human puts garbage into the test, the test will return garbage out.

@@

My system's output could be converted into some actionable, useful response with an output parser, 
and then passed back to the AI agent. For example, if the AI agent is equipped to evaluate natural 
language prescriptions, the status of the maxim could be parsed into a natural language sentence. The 
input parser, categorical imperative library, and output parser together constitute an ``ethics engine'' 
that AI developers could use as a black box implementation of an ethical theory.

@@

Consider the example badly-formed maxim, ``When eating breakfast, I will eat breakfast in order to 
eat breakfast.'' There is something empty about this maxim because acting on it could never result in 
any action. If an agent adopts this maxim, 
they decide that, in the circumstances ``eating breakfast'' they will perform the act ``eating breakfast''
for the purpose ``eating breakfast.'' In these circumstances, the act has 
already been performed. Adopting this maxim as a law to live by does not change how you live. If you adopt 
this maxim, then when you are eating breakfast, you eat breakfast, but this statement is already tautologically true.

@@

Another related worry concerns maxims that we think are prohibited. Consider the maxim modified to 
read ``When dancing and seeing a child drowning, I should dance for the sake of dancing.'' Clearly this 
maxim is fit for moral evaluation, and we expect a moral theory to prohibit this maxim. The circumstances 
``When dancing and seeing a child drowning'' appear to entail the act of dancing, and the maxim thus 
appears badly-formed. Once again, this maxim is formulated incorrectly. In this case, the question 
that the agent is actually asking themselves is ``should I continue dancing?'' That is the 
maxim that they will adopt or reject. They want to know if they should stop dancing and go help the child. 
Dancing at the current moment and dancing at the next moment are different acts, and the circumstances 
imply the former but not the latter. A badly-formed maxim would have circumstances and act both 
``dancing at moment t,'' but this maxim has circumstances ``dancing at moment t'' and act ``dancing 
at moment t+1.''

@@

Above, I defined badly formed maxims, a philosophical concept that I discovered
using computational ethics. In this section, I explore the implications of this concept for a 
philosophical debate to show that computational ethics can result in insights with real 
philosophical weight. I use badly formed maxims to resolve the tension between self-doubt and self-respect. 
This debate originated in epistemology, which values doubting your beliefs but also rationally requires
that you believe that you are not mistaken (else you should update your beliefs). 
Self-doubt and self-respect also compete in ethics, where questioning your judgements is valuable but 
questioning a commitment as you make it is impossible. Self-doubt and self-respect appear 
irresolvably opposed until they are understood through the lens of badly formed maxims. I argue that naive
conceptions of self-doubt are badly formed maxims in disguise. If we reformulate these maxims to be well-formed,
the tension between self-doubt and self-respect dissolves, and it becomes clear that both concepts can
co-exist, as we intuitively desire. I sketch the details of this argument in the rest of this section.

@@

While most philosophers accept some version of SR\footnote{Christensen cites \citet{vanfraassen}, 
\citet{vickers}, and \citet{koons}.}, 
Roush argues that the principle must be modified in order to account for healthy epistemic 
self-doubt. She argues that, while pathological second-guessing is correctly criticized, we are generally 
imperfect beings, and some sensitivity to our own limitations is a virtue \cite[2]{roushselfhelp}. Even Christensen 
acknowledges that total self-confidence is an epistemic flaw \cite[1]{christensen}. Thus, there is tension between the rational
requirement to respect our authority as believers and the practical reality that we are often wrong.

@@

To resolve this tension, I return to my earlier example of a dancer. Imagine Sara is dancing at a 
weddding, when, in a moment of angst, she asks herself, ``Should I really be dancing right now?'' 
It seems that she asking if the maxim, ``When dancing at your friend's wedding, dance for the sake 
of dancing'' is a permissible maxim to act on. Notice that the maxim in question is badly-formed: the 
circumstance ``when dancing at a friend's wedding'' implies the act ``dance.'' As I argued above, if 
Sara asks if she should will a badly formed maxim, she is questioning her own will's authority, which
is paradoxical. If maxims are about self-doubt are badly-formed maxims, then the tension between ESR
and ESD is natural and unavoidable: debating the permissibility of a badly-formed maxim inherently
involves questioning commitments as we make them, which is impossible. This is the source of the 
tension between ESR and ESD. Those committed to this 
interpretation must abandon one principle or the other, since committing and questioning are incompatible.

To resolve this issue, I turn to another interpretation of ethical self-doubt. Under this interpretation, 
when Sara asks, ``Should I really be dancing right now?'' she wants to know if the maxim that 
resulted in the current moment when she is on the dance floor was the right thing to will. She is 
asking if she made the right decision in the past, when she decided to dance. The maxim that initiated 
the dancing may be something like ``When at a wedding, dance for the sake of dancing.'' This is the maxim 
that she is currently acting on, not the badly-formed maxim  from above. Under this interpretation, 
there is no tension at all between self-doubt and self-respect. It is perfectly valid for a reasoner 
to doubt their prior moral judgements, just as it is perfectly rational for a believer to doubt their 
past beliefs \cite[3-4]{christensen}. Such doubt does not undermine the reasoner's decision-making 
capacity and is thus perfectly consistent with ethical self-respect. Moreover, this is a much more 
intuitive question to be asking \emph{because} it is a well-formed maxim. Not only is the badly-formed
interpretation of this maxim problematic for ESR, it is also not the kind of question that is useful for a practical
reasoner to ask, as argued above.

Thus, the tension between ESR and ESD arises from a misreading of questions of self-doubt as questions about 
the evaluation of badly-formed maxims. A question of self-doubt cannot refer to a badly-formed maxim and must 
instead refer to a well-formed maxim about the agent's past decision-making. As seen before, cases where 
agents appear to ask themselves about badly-formed maxims are mistaken about the maxim in question, because 
such a question could never yield a useful answer for a practical reasoner.

By recognizing that the naive version of ethical self-doubt is a badly formed maxim, I realized 
that there is something wrong with its formulation and modified it to resolve the above debate. 
This demonstrates a larger meta-pattern in Kantian reasoning: many debates in Kantian philosophical
literature revolve around incorrectly formulated maxims, so the insight about badly
formed maxims is significant. Much of the work of a Kantian ethicist is formulating an
appropriate maxim, and badly-formed maxims define one boundary condition for this task. Just as my isolation
of the wrongness of lying in Section \ref{joking} could help guide the formation of morally worthy maxims, 
so can the insight about badly-formed maxims.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{An Argument For Computational Ethics%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
The insight above is an example of the kind of philosophical progress that can be 
made using computational tools and serves as evidence for the power of computational ethics. The 
idea that the FUL can only hold for well-formed maxims would have been
incredibly difficult to discover without a computer. I discovered it while formulating the FUL because 
Isabelle's proof-finding tools look for edge cases like badly-formed maxims. Badly-formed maxims are 
interesting because they are the kind of thing that is usually ignored in ordinary philosophical inquiry. 
Philosophers usually assume that we are not discussing badly-formed maxims because, as argued above, 
they are not the kind of thing that is immediately relevant to ethics. Computational tools like Isabelle
require that assumptions like the exclusion of well-formed maxims are made precise, and thus force 
philosophers to understand their arguments in a new way. This example demonstrates the contributions
that computational ethics makes: it can quickly check edge cases and it requires that all assumptions be
made explicit and precise.

I do not argue that computational ethics uncovers philosophical insights that humans are incapable 
of reaching. Instead, I claim that insights like the one about the well-formed maxim are much easier
to reach with computational tools. Computational 
tools prompt philosophers to ask new questions that 
lead to insights, and can thus serve as another tool in a philosopher's arsenal, like a 
thought experiment or counterexample.\footnote{Even if computational ethics is possible, some may 
worry that it sacrifices something important about philosophical inquiry. I discuss this concern in Appendix 
\ref{academicphilosophy}.}

@@

Computational ethics is at its infancy. The use of theorem provers in mathematics is just now beginning 
to make headway \citep{buzzardvideo}, even though theorem provers were first invented in the 1960's \citep{historyofITP}. 
In contrast, the first attempts to use theorem provers for ethics occurred in the last few years. The 
fact that this nascent technology is already helping humans reach non-trivial philosophical conclusions 
is reason to, at the very least, entertain the possibility of a future where computational ethics 
becomes as normal for philosophers as using a thought experiment.

@@

The above model of human-computer symbiosis demonstrates how computational ethics can augment human
ethical reasoning without replacing it. When deliberating over moral dilemmas, ordinary people can 
turn to computational tools for advice, like an ``Ask an Ethicist'' column. If we appeal to philosophically
faithful computational ethics like that implemented in this thesis, then this advice will synthesize 
decades of philosophical progress and is thus a way to apply philosophers' insights to ordinary life. 
Moreover, just as they do for philosophers, computers can help ordinary people approach ethical questions from a 
different perspective. Even interacting with my system requires the user to consider the action's maxim, 
which includes the circumstances, act, and goal. Making these components of action precise already changes
the user's perspective. Just as computational ethics can serve as a tool for academic philosophers to 
automate away tedium and achieve greater precision, it can do the same for ordinary human beings navigating
the world. Moreover, it also offers another way for the general public to access professional philosophy
insights, and thus carries potential to improve our everyday reasoning.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Theoretical Objections to Automating Kantian Ethics \label{amapossible}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Many philosophers cringe at the idea that a computer could perform ethical reasoning or that the 
categorical imperative could provide an algorithm for moral judgement. For example, Rawls asserts, 
``it is a serious misconception to think of the CI-procedure as an algorithm intended to yield, 
more or less mechanically, a correct judgment. There is no such algorithm, and Kant knows this'' \citep[166]{rawlslectures}. 
Ebels-Duggan also claims, ``no one supposes that the Categorical Imperative provides a mechanical 
algorithm that delivers all by itself a complete account of what we ought to do in any given 
situation'' \citep[174]{ebelsduggan}. However unmechanical ethical reasoning
may seem, these claims are not obvious and require further justification. Philosophers who believe 
that mental activity completely determines moral reasoning must explain why computers can, in theory, 
simulate certain mental processes like arithmetic and language, but cannot perform ethical reasoning. 
Without a soul or God-based account of ethical reasoning, it is not obvious that it is theoretically 
impossible to automate ethical reasoning. After all, computers may eventually learn to simulate human 
mental activity entirely, as shown by progress in brain simulation \citep{brainsimulation}.

@@

In \emph{Universal Laws and Ends In Themselves}, O'Neill argues against the existence of an algorithm for
moral behavior. She points out that Kant draws an important distinction between a morally worthy maxim
and a morally worthy action: the latter requires a good will, or a will motivated by duty. She argues that, 
``Kant defines duty not (as would be common today) as outward performance of a certain sort, but as action
that embodies a good will'' \citep[345]{oneilluniversallaws}. Moral behavior doesn't just require performing
a ``good'' action, but it requires acting on a morally worthy maxim from the motivation of duty, or 
doing the right thing because it is the right thing to do. It is this capacity 
for self-motivation that makes morality binding for rational beings; we must behave morally precisely 
because we have wills, or the ability to be motivated by ends
that we choose. Only rational beings have wills, so only rational beings can have good wills, or wills
motivated by duty, and thus only rational beings can behave morally. Under this understanding
of moral behavior, it seems unlikely that a computer could behave morally
since a computer does not have motivation in the same way as a human being. If a computer is not a fully rational
being, then it is not the kind of thing that can behave morally.\footnote{A parallel argument can also be made for virtue ethics. Virtuous
behavior requires not only a certain action, but also a certain disposition towards the action, so it seems
difficult for an AI agent to truly behave virtuously.}

@@

The challenge of mapping actions to maxims is a limitation of my system, but it is not insurmountable. In Section \ref{AIethics},
I argued that, before my system can be used in practice, it must be paired with an input parser that can
translate choices that an automated agent faces into maxims in a logic that my system can
evaluate. This need follows from the difficulty in mapping a potential action
to the maxim of action, whether concerning human action or machine action. As argued in Section \ref{AIethics},  
this is not an insurmountable obstacle for automated ethics and heuristic-based approaches could resolve
this issue. Determining the maxim of action is a challenge for Kantian human beings \citep{oneilluniversallaws}, 
so it is unsurprising that it is a major hurdle for automated Kantian agents.

@@

%:%61=32%:%

@@

%:%174=144%:%
%:%183=146%:%

@@

%:%199=152%:%
%:%208=154%:%

@@

%:%402=338%:%
%:%403=339%:%
%:%404=340%:%
%:%405=341%:%
%:%406=342%:%
%:%415=346%:%

@@

%:%488=409%:%
%:%489=410%:%
%:%490=411%:%
%:%491=412%:%
%:%500=414%:%

@@

%:%587=491%:%
%:%588=492%:%
%:%589=493%:%
%:%590=494%:%
%:%599=497%:%

@@

%:%715=604%:%
%:%716=605%:%
%:%717=606%:%

@@

%:%723=611%:%
